---
title: ""
author: "Mario"
date: '2021-03-16'
output: html_document
---
## Shrub Density influences on Animals
The following is a review of shrubs that have been reported as benefactor species on local animal communities. Web of Science resources were queried using the following key terms.

"facil* density* shrub*”, “density* shrub* facilitate*” and “density* shrub* animal* facil*"

### Questions:
Is there evidence that shrub studies that reported facilitation of other plants or of animals influence measures of animal community composition?  
Is there are a relationship between animal abundance or richness and shrub or tree density?
Is there a difference between the measures of animal community composition in studies that reported facilitation or not?

### Hypothesis:
Higher density of foundation species that have reported facilitation support higher densities or more rich animal communities.

### Predictions:
1. Reported benefactor plants better support animal communities.  
2. Higher density of benefactor plants predict higher measures of animal community structure or composition.  

```{r setup, include=FALSE}
library(tidyverse)
library(stats)
library(RColorBrewer)
library(ggpubr) 
data <- read_csv("Synthesis Data.csv") %>%
  rename(abundance = "animal.abundance") %>%
  rename(density = "density.number")
data

###Abundance
library(metafor)
data_e1 <- escalc(measure = "IR", xi = abundance, ti = n_days, ni = standardized.density, data = data) %>% 
  filter(yi != "NA")

data_e2 <- escalc(measure = "IR", xi = animal.richness, ti = density, data = data) %>% 
  filter(yi != "NA")

###Rename the new columns
data_1 <- data_e1 %>% 
  rename(abundance_rate = yi, var_abundancerate = vi)

data_2 <- data_e2 %>%
  rename(richness_rate = yi, var_richnessrate = vi)

###All data
data_all <- merge(data_1, data_2, all = TRUE)

###Summarize Data
summary_data <- data_all %>% 
  group_by(Study.ID) %>% 
  summarise(abundance = mean(abundance), density = mean(standardized.density), abundance_rate = mean(abundance_rate), var_abundance= sd(var_abundancerate))
summary_data$Study.ID <- as.character(summary_data$Study.ID)

#Make the weight for the regression
summary_data$W <- 1/summary_data$var_abundance^2

#Not usefull#
summary_data2 <- data_all %>% 
  group_by(macrohabitat) %>% 
  summarise(abundance = mean(abundance), abundance_rate = mean(abundance_rate), richness_rate = mean(richness_rate), var_abundance= sd(var_abundancerate), var_richnessrate = sd(var_richnessrate), mean_density= mean(standardized.density))
summary_data$Study.ID <- as.character(summary_data$Study.ID)


data
```

### Good Figures (June 8th 2021)
```{r}
ggplot(data = data_e1, aes(yi)) +
  geom_histogram(bins = 40) + labs(x = "Incidence Rate for Animal Abundance", y = "Frequency") + theme_classic()
```

```{r}
ggplot(summary_data, aes(Study.ID, abundance_rate)) +
  geom_point(size =2) +
  geom_errorbar(aes(ymin = abundance - var_abundance, ymax = abundance + var_abundance), size= 0.7, width=0.1, position = position_dodge(width = 0.5)) +
  coord_flip() +
  geom_hline(yintercept = 1, colour="grey", linetype = "longdash", size = 2) + 
  labs(x = "Study", y = "Incident Rate of Abundance") + theme_classic()
```

### Meta Models
```{r}
library(broom)
#x = density
#y = abundance
#With density
mod1.1 <- rma(yi = yi, sei = vi, method = "ML", test = "knha", control=list(stepadj=0.5), data = data_e1)
summary(mod1.1)
```
```{r}
mod1.2 <- rma(yi = yi, sei = vi, method = "ML", mods = ~macrohabitat-1, test = "knha", control=list(stepadj=0.5), data = data_e1)
summary(mod1.2)
```


```{r}
m1.1 <- tidy(mod1.1) 
m1.1
```
```{r}
plot(mod1.1)
```

###Weighted regression with all data
```{r}
gmodel <- lm(standardized.density ~ abundance, data=data_all, weights = n_days)
gmodel
summary(gmodel)
```
### Fig1 with Line
```{r}
ggplot(data = data_e1, aes(abundance, standardized.density)) +
  geom_point() +
  geom_smooth(method = "lm", mapping = aes(weight = n_days), se = F) + labs(x = "Abundance", y = "Density") + theme_classic()
```
### Fig1 With Curve
```{r}
fig1 <- ggplot(data = data_e1, aes(abundance, standardized.density, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Abundance", y = "Density") + theme_classic() + facet_wrap(~macrohabitat)
fig1
```
```{r}
color_points <- ggplot(data = data_e1, aes(abundance, standardized.density, color = macrohabitat)) +
  geom_point() + scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue"))
color_points + theme(legend.title = element_blank()) + labs(x = "Abundance", y = "Density") +theme_classic()
```



```{r}
model1 <- lm(standardized.density ~ abundance, data=data_all)
summary(model1)
```
```{r}
plot(fitted(model1), resid(model1), xlab='Fitted Values', ylab='Residuals') + abline(0,0)
```
```{r}
library(lmtest)
bptest(model1)
```
```{r}
wt <- 1 / lm(abs(model1$residuals) ~ model1$fitted.values)$fitted.values^2
wls_model <- lm(standardized.density ~ abundance, data = data_all, weights=wt)
summary(wls_model)
```
```{r}
data.frame(y = rstandard(model1),
           x = model1$fitted.values) %>%
  ggplot(aes(x = x, y = y)) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(title = "Standardized Residuals vs Fitted Values Plot")
```
```{r}
ggplot(data = data_all, aes(y = standardized.density, x = abundance)) +
  geom_point() +
  geom_smooth(method = lm, se = FALSE,
              color = "black", 
              size = 0.5, 
              linetype = "dashed") +
  geom_smooth(method = lm, se = FALSE, 
              aes(weight = wt),
              color = "red", 
              size = 0.5,
              linetype = "dashed") +
  labs(title = "Scatterplot of Density ~ abundance")
```
















###Trying to do regressions with summary data
```{r}
cmodel <- lm(density ~ abundance_rate, data=summary_data, weights = )
cmodel
```
```{r}
summary(cmodel)
```


```{r}
ggplot(data = summary_data, aes(abundance, density)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
model <- lm(density ~ abundance, data=data_e1)
summary(model)
```
```{r}
plot(fitted(model), resid(model), xlab='Fitted Values', ylab='Residuals') + abline(0,0)
```
```{r}
library(lmtest)
bptest(model)
```
```{r}
wt <- 1 / lm(abs(model$residuals) ~ model$fitted.values)$fitted.values^2
wls_model <- lm(density ~ abundance, data = data_e1, weights=wt)
summary(wls_model)
```

```{r}
data.frame(y = rstandard(model),
           x = model$fitted.values) %>%
  ggplot(aes(x = x, y = y)) + 
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  labs(title = "Standardized Residuals vs Fitted Values Plot")
```


```{r}
#Sampling effort
ggplot(data_e1, aes(n_days, yi)) +
  geom_point(aes(color = macrohabitat)) + 
  labs(x = "total days sampled per study", y = "abundance capture rates")
```

```{r}
MyData <- read.csv("MyData.csv")

```
```{r}
###Forest Plot for paper
figure3 <- ggplot(data_all, aes(as.factor(rep), abundance_rate, color = macrohabitat)) +
  geom_point(size =2) +
  geom_errorbar(aes(ymin = abundance_rate - var_abundancerate, ymax = abundance_rate + var_abundancerate), size= 0.4, width=0.1, position = position_dodge(width = 0.5)) +
  coord_flip() +
  geom_hline(yintercept = 1, colour="grey", linetype = "longdash", size = 0.5) + 
  labs(x = "Rep", y = "Incident Rate of Abundance") + theme_classic() + 
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(),legend.title = element_blank(), axis.text = element_text(size = 10)) + labs(x = "Observations") + scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + facet_wrap(~macrohabitat)
  
figure3
```
```{r}
gd <- data_all %>% group_by(macrohabitat) %>%
  summarise(abundance_rate = mean(abundance_rate), rep = rep/rep)
grassland <- gd[-c(1:39),]
desert <- gd[-c(40:113),]
```



```{r}
desert.forest <- ggplot(subset(data_all, macrohabitat %in% c("desert")), aes(as.factor(rep), abundance_rate, color = macrohabitat)) + 
  geom_point(size =2) +
  geom_errorbar(aes(ymin = abundance_rate - var_abundancerate, ymax = abundance_rate + var_abundancerate), size= 0.4, width=0.1, position = position_dodge(width = 0.5)) +
  coord_flip() + facet_wrap(~microsite, scales = "free") +
  geom_hline(yintercept = 1, colour="grey", linetype = "longdash", size = 1.5) + 
  labs(x = "Rep", y = "Incident Rate of Abundance") + theme_classic() + 
  theme(legend.position = "none", axis.text.y = element_blank(), axis.ticks.y = element_blank(),legend.title = element_blank(), axis.text = element_text(size = 10)) + labs(x = "Observations") + scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + facet_wrap(~macrohabitat, scales = "free") + geom_point(data = desert, size = 5, shape = "triangle")+scale_y_continuous(breaks=c(0,2,4,6,8))
desert.forest 
```
```{r}
grassland.forest <- ggplot(subset(data_all, macrohabitat %in% c("grassland")), aes(as.factor(rep), abundance_rate, color = macrohabitat)) +
  geom_point() +
  geom_errorbar(aes(ymin = abundance_rate - var_abundancerate, ymax = abundance_rate + var_abundancerate), size= 0.4, width=0.1, position = position_dodge(width = 0.5)) +
  coord_flip() + facet_wrap(~microsite, scales = "free") +
  geom_hline(yintercept = 1, colour="grey", linetype = "longdash", size = 1.5) + 
  labs(x = "Rep", y = "Incident Rate of Abundance") + theme_classic() + 
  theme(axis.title.y = element_blank(), axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = "none", legend.title = element_blank(), axis.text = element_text(size = 10)) + labs(x = "Observations") + scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + facet_wrap(~macrohabitat, scales = "free") + geom_point(data = grassland, size = 5, shape = "triangle")
grassland.forest
```

```{r}
###Figure is good! :D
forestfig <- ggarrange(desert.forest, grassland.forest, nrow = 1, align = "v", heights = 10)
forestfig
```
```{r}
### Has abundance on x axis so does not work!!!
grassland <- ggplot(subset(data_e1, macrohabitat %in% c("grassland")), aes(abundance, standardized.density, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Animal Abundance", y = "Shrub Density") + theme_classic() + scale_color_manual(values = c("grassland" = "dark blue")) +theme(legend.position = "none") 
grassland
```
```{r}
### Has abundance on x axis so does not work!!!
desert <- ggplot(subset(data_e1, macrohabitat %in% c("desert")), aes(abundance, standardized.density, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Animal Abundance", y = " Shrub Density") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none") + ylim(0,15)
desert
```
```{r}
scatterplot <- ggarrange(desert, grassland, nrow = 1, align = "v", heights = 10)
scatterplot
```

##Try with natural log (Do not use this!)
```{r}
data_1$natlog <- log(data_1$abundance)
log.grassland <- ggplot(subset(data_1, macrohabitat %in% c("grassland")), aes(standardized.density, natlog,  color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density", y = "Log Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) +theme(legend.position = "none")

log.desert <- ggplot(subset(data_1, macrohabitat %in% c("desert")), aes(standardized.density, natlog, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density", y = "Log Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none")
```
```{r}
logplot <- ggarrange(log.desert, log.grassland, nrow = 1, align = "v", heights = 10)
logplot
```
```{r}
data_1$natlog.dense <- log(data_1$standardized.density)
log.grassland.dense <- ggplot(subset(data_1, macrohabitat %in% c("grassland")), aes(natlog.dense, abundance,  color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Log Shrub Density", y = "Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) +theme(legend.position = "none")

log.desert.dense <- ggplot(subset(data_1, macrohabitat %in% c("desert")), aes(natlog.dense, abundance, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Log Shrub Density", y = "Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none")
logplot.dense <- ggarrange(log.desert.dense, log.grassland.dense, nrow = 1, align = "v", heights = 10)
logplot.dense
```


```{r}
Alex_paper <- read.csv("Carrizo_telemetry_with_shrub_density.csv")
Alex_paper_mean <- aggregate(Alex_paper[, 10], list(Alex_paper$year), mean)

Alex_paper_count <- Alex_paper %>%
 count(year, lizard)

library(dplyr)
Alex_paper_count <- Alex_paper_count %>% 
  group_by(year) %>% 
  summarise(Sum = sum(n))
colnames(Alex_paper_mean) <- c("year", "Average Density")

Alex_final <- merge(Alex_paper_mean, Alex_paper_count)

Test <- Alex_paper %>%
 count(lizard, year)
```


```{r}
###Figures have density on x axis
desertnew <- ggplot(subset(data_e1, macrohabitat %in% c("desert")), aes(standardized.density, yi, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density", y = " Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none")
desertnew

grasslandnew <- ggplot(subset(data_e1, macrohabitat %in% c("grassland")), aes(standardized.density, yi, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density", y = " Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none")
grasslandnew
```
```{r}
scatterplotnew <- ggarrange(desertnew, grasslandnew, nrow = 1, align = "v", heights = 10)
scatterplotnew
```
```{r}
log.facet <- ggplot(data_1, aes(standardized.density, natlog,  color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density", y = "Log Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) +theme(legend.position = "none")
log.facet
```
```{r}
plot <- ggplot(data_e1, aes(standardized.density, yi, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x +I(x^2), mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density", y = "Animal Abundance") + theme_classic() + facet_wrap(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none")
plot
```
```{r}
###Main figure!
library(scales)
yi.plot <- ggplot(data_e1, aes(standardized.density, yi, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density (per km^2)", y = "Animal Abundance") + theme_classic() + facet_grid(~macrohabitat, scales = "free")+ scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none") +  scale_y_continuous(breaks= pretty_breaks())
yi.plot
```
```{r}
####Testing main data with no zeros

exampleDF <- data_e1 %>%
  group_split(zeroes = standardized.density == 0 | yi == 0)

nozeros <- ggplot(exampleDF[[1]], aes(x = standardized.density, y = yi)) + 
  geom_smooth(method = "lm", formula = y~x, mapping = aes(weight = n_days), se = F)  + 
  geom_point() +
  geom_point(data = exampleDF[[2]], aes(x = standardized.density, y = yi), color = "red") +
  xlab("Shrub Density") + 
  ylab("Abundance")
nozeros
```


```{r}
yi.plot <- ggplot(data_e1, aes(standardized.density, yi, color = macrohabitat)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, mapping = aes(weight = n_days), se = F) + labs(x = "Shrub Density (per km^2)", y = "Animal Abundance") + theme_classic() + scale_color_manual(values = c("desert" = "red", "grassland" = "dark blue")) + theme(legend.position = "none")
yi.plot
```


```{r}
data_new <- data_e1 %>% filter(plant.species !="Unknown")

Caragana.K <- ggplot(subset(data_new, plant.species %in% c("Caragana korshinskii")), aes( standardized.density, yi, color = plant.species)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, mapping = aes(weight = n_days), se = F) + labs(x = "", y = "Animal Abundance") + theme_classic() + facet_wrap(~plant.species) + scale_color_manual(values = c("Caragana korshinskii" = "dark blue")) + theme(legend.position = "none") +  scale_y_continuous(breaks= pretty_breaks())
Caragana.K

Caragana.M <- ggplot(subset(data_new, plant.species %in% c("Caragana microphylla")), aes( standardized.density, yi, color = plant.species)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, mapping = aes(weight = n_days), se = F) + labs(x = "", y = " ") + theme_classic() + facet_wrap(~plant.species) + scale_color_manual(values = c("Caragana microphylla" = "red")) + theme(legend.position = "none") + ylim(0,0.05) + scale_y_continuous(breaks = pretty_breaks()) 
Caragana.M

Ephedra<- ggplot(subset(data_new, plant.species %in% c("Ephedra californica")), aes( standardized.density, yi, color = plant.species)) +
  geom_point() +
  geom_smooth(method = "lm", formula = y~x, mapping = aes(weight = n_days), se = F) + labs(x = "", y = "") + theme_classic() + facet_wrap(~plant.species)  + scale_color_manual(values = c("Ephedra californica" = "red")) + theme(legend.position = "none") + scale_y_continuous(breaks = pretty_breaks()) 
Ephedra

fig3 <- ggarrange(Caragana.K, Caragana.M, Ephedra, ncol = 2, nrow = 2)
fig3 <- annotate_figure(fig3, bottom = text_grob("Shrub Density (per km^2)", 
               color = "black", face = "bold", size = 10))
fig3
```
```{r}
###By shrub species
mod1.3 <- rma(yi = yi, sei = vi, method = "ML", mods = ~plant.species-1, test = "knha", control=list(stepadj=0.5), data = data_new)
summary(mod1.3)
```


### Interpretations
1) Density matters in both grasslands and deserts
2) The net effect of increasing density is positive and it's significantly positive (1.92)
