---
title: ""
author: "Mario"
date: '2021-03-16'
output: html_document
---
## Shrub Density influences on Animals
The following is a review of shrubs that have been reported as benefactor species on local animal communities. Web of Science resources were queried using the following key terms.

"facil* density* shrub*”, “density* shrub* facilitate*” and “density* shrub* animal* facil*"

### Questions:
Is there evidence that shrub studies that reported facilitation of other plants or of animals influence measures of animal community composition?  
Is there are a relationship between animal abundance or richness and shrub or tree density?
Is there a difference between the measures of animal community composition in studies that reported facilitation or not?

### Hypothesis:
Higher density of foundation species that have reported facilitation support higher densities or more rich animal communities.

### Predictions:
1. Reported benefactor plants better support animal communities.  
2. Higher density of benefactor plants predict higher measures of animal community structure or composition.  

```{r setup, include=FALSE}
library(tidyverse)
data <- read_csv("Synthesis Data.csv") %>%
  rename(abundance = "animal.abundance") %>%
  rename(density = "density.number")
data

###Abundance
library(metafor)
data_e1 <- escalc(measure = "IR", xi = abundance, ti = standardized.density, data = data) %>% 
  filter(yi != "NA")

###Richness (Not useful since only 1 study reports richness)
data_e2 <- escalc(measure = "IR", xi = animal.richness, ti = density, data = data) %>% 
  filter(yi != "NA")

###Rename the new columns
data_1 <- data_e1 %>% 
  rename(abundance_rate = yi, var_abundancerate = vi)

data_2 <- data_e2 %>%
  rename(richness_rate = yi, var_richnessrate = vi)

###All data
data_all <- merge(data_1, data_2, all = TRUE)

###Summarize Data
summary_data <- data_all %>% 
  group_by(Study.ID) %>% 
  summarise(abundance = mean(abundance), abundance_rate = mean(abundance_rate), richness_rate = mean(richness_rate), var_abundance= sd(var_abundancerate), var_richnessrate = sd(var_richnessrate), mean_density= mean(standardized.density))
summary_data$Study.ID <- as.character(summary_data$Study.ID)
#Not usefull#
summary_data2 <- data_all %>% 
  group_by(macrohabitat) %>% 
  summarise(abundance = mean(abundance), abundance_rate = mean(abundance_rate), richness_rate = mean(richness_rate), var_abundance= sd(var_abundancerate), var_richnessrate = sd(var_richnessrate), mean_density= mean(standardized.density))
summary_data$Study.ID <- as.character(summary_data$Study.ID)
```

### Good Figures (May 18 2021)
```{r}
ggplot(data = data_e1, aes(yi)) +
  geom_histogram(bins = 40) + labs(x = "Incidence Rate for Animal Abundance", y = "Frequency") + theme_classic()
```

```{r}
ggplot(summary_data, aes(Study.ID, abundance_rate)) +
  geom_point(size =2) +
  geom_errorbar(aes(ymin = abundance - var_abundance, ymax = abundance + var_abundance), size= 0.7, width=0.1, position = position_dodge(width = 0.5)) +
  coord_flip() +
  geom_hline(yintercept = 1, colour="grey", linetype = "longdash", size = 2) + 
  labs(x = "Study", y = "Incident Rate of Abundance") + theme_classic()
```

### Meta Models
```{r}
library(broom)
#x = density
#y = abundance
#With density
mod1.1 <- rma(yi = yi, sei = vi, method = "ML", mods = ~standardized.density, test = "knha", control=list(stepadj=0.5), data = data_e1)
summary(mod1.1)
```
```{r}
m1.1 <- tidy(mod1.1)
m1.1
```
```{r}
plot(mod1.1)
```

### Interpretations
