---
title: ""
author: "Mario"
date: '2021-03-16'
output: html_document
---
##Shrub Density influences on Animals
The following is a review of shrubs that have been reported as benefactor species on local animal communities. Web of Science resources were queried using the following key terms.

"facil* density* shrub*”, “density* shrub* facilitate*” and “density* shrub* animal* facil*"

###Questions:
Is there evidence that shrub studies that reported facilitation of other plants or of animals influence measures of animal community composition?  
Is there are a relationship between animal abundance or richness and shrub or tree density?
Is there a difference between the measures of animal community composition in studies that reported facilitation or not?

###Hypothesis:
Higher density of foundation species that have reported facilitation support higher densities or more rich animal communities.

###Predictions:
1. Reported benefactor plants better support animal communities.  
2. Higher density of benefactor plants predict higher measures of animal community structure or composition.  

```{r setup, include=FALSE}
library(tidyverse)
data <- read_csv("Synthesis Data.csv") %>%
  rename(abundance = "animal.abundance") %>%
  rename(density = "density.number")
data

###Abundance
library(metafor)
data_e1 <- escalc(measure = "IR", xi = abundance, ti = density, data = data) %>% 
  filter(yi != "NA")

###Richness
data_e2 <- escalc(measure = "IR", xi = animal.richness, ti = density, data = data) %>% 
  filter(yi != "NA")

###Rename the new columns
data_1 <- data_e1 %>% 
  rename(abundance_rate = yi, var_abundancerate = vi)

data_2 <- data_e2 %>%
  rename(richness_rate = yi, var_richnessrate = vi)


###All data
data_all <- merge(data_1, data_2, all = TRUE)

###Summarize Data
summary_data <- data_all %>% 
  group_by(Study.ID) %>% 
  summarise(abundance = mean(abundance), abundance_rate = mean(abundance_rate), richness_rate = mean(richness_rate), var_abundance= sd(var_abundancerate), var_richnessrate = sd(var_richnessrate), mean_density= mean(density))
```

###Meta Models
```{r}
library(broom)
#x = density
#y = abundance

mod1.1 <- rma(yi = yi, sei = vi, method = "ML", mods = ~density, test = "knha", control=list(stepadj=0.5), data = data_e1)
summary(mod1.1)
```
```{r}
m1.1 <- tidy(mod1.1)
m1.1
```
```{r}
plot(mod1.1)
```


```{r}
mod1.2 <- rma(yi = yi, sei = vi, method = "ML", mods = ~macrohabitat -1, test = "knha", control=list(stepadj=0.5), data = data_e1)
summary(mod1.2)
```
```{r}
m1.2 <- tidy(mod1.2)
m1.2
```
```{r}
plot(mod1.2)
```

###Data Viz 
```{r}
ggplot(summary_data, aes(abundance, mean_density)) +
  geom_point() +
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 2, color = "black", size = 2, se = FALSE)
```

```{r}
ggplot(data_e1, aes(macrohabitat, yi)) +
  geom_boxplot() +
  labs(x = "ecoystem", y = "abundance animals") + 
  stat_summary(fun.y=mean, geom="point", shape=1, size = 1, color="black", fill="red")
```

```{r}
ggplot(data_e1, aes(density, abundance)) +
  geom_point(aes(color = macrohabitat)) + 
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 2, color = "black", se = FALSE) +
  labs(x = "density", y = "abundance")
```

###Interpretations
